---
title: "Assignment 1"
author: "Ziya YİĞİT"
date: "19 01 2022"
output: word_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) #deleting plot warning messages
```

```{r set-options, echo= FALSE, cache= FALSE}
options(width = 250)                           #width problem, cannot see BMI and BMI type, does not fit the screen
```                                           

```{r include = FALSE}
library(tidyverse)
library(knitr)
```

### Q1 : How many characters do have at least one starship? List the names of the characters having at least one starship.


```{r include = FALSE}
starship_owners<-filter(starwars,starships != "character(0)")
lengths1<-length(starship_owners$name)
names1<-select(starship_owners,name,starships)
```
There are `r lengths1` characters who have at least one starship.

```{r echo=FALSE}
kable(names1)
```
### Q2 : Get the frequencies of the eye color of the characters. Rank them from most to least.

```{r echo = FALSE}
eyecolor_frequency<-starwars %>%
  group_by(eye_color) %>%
  summarize(
    count=n()
  )
kable(arrange(eyecolor_frequency,desc(count)))
```

### Q3 : According to the data available, what are the average age values across each species? Find the 3 oldest species.

```{r echo = FALSE}
delete_nas = filter(starwars, birth_year != "NA")

mean_age<-delete_nas %>%
  group_by(species) %>%
  summarize(
    age_mean=mean(birth_year)
  )

specs_mean_age<-arrange(mean_age,desc(age_mean))

kable(specs_mean_age[c(1,2,3),])
```

### Q4. Create a new data set by adding a new observation to this data.

```{r echo = FALSE}
starwars_with_me<-rbind(starwars,c("Darth Ziya",188,100,
                                   "brown","green","black",21.0,"male",
                                   "masculine","Tatooin","Human",
                                   "Revenge of the Sith",
                                   "Jedi Fighter","Death Star"))


starwars_with_me$height<- as.integer(starwars_with_me$height) #error fix non
starwars_with_me$mass<- as.double(starwars_with_me$mass)      #numeric to binary

kable(tail(starwars_with_me,1))
```

### Q5. Calculate the body mass index (BMI) values (dividing the mass value in kg to the square of the height value in meter) for all observations and categorize the observations as underweight (BMI below 18.5), healthy (BMI between 18.5-24.99), overweight (BMI between 25.0-29.99) and obese (BMI above 30.0). Add these two variables to your new data created at the 4th question.

```{r echo = FALSE}
starwars_with_me<-starwars_with_me %>%
  mutate(name,BMI=mass/((height/100)^2))

starwars_with_me<-starwars_with_me %>%
  mutate(name,health_hype = if_else(BMI<18.5, "underweight",
                                    if_else(BMI<25,"healthy",
                                            if_else(BMI<30,"overweight",
                                                    "obese"))))
kable(head(starwars_with_me,2))
```

### Q6. Plot the distribution of ages less than 100 by BMI groups. (i.e. use filter function to select the ages less then 100)
```{r echo = FALSE,message=FALSE,warning=FALSE,comment=FALSE}
starwars_with_me$birth_year<-as.integer(starwars_with_me$birth_year)
age_below_hundred<-filter(starwars_with_me,birth_year<100.0)

ggplot(data=age_below_hundred)+
  geom_boxplot(mapping=aes(x=health_hype,y=birth_year))

```
Figure 1. The distribution of ages less than 100 by BMI groups


### Q7. By plotting a graph, show the relationship between age and BMI values (use point and line at the same time).

```{r echo = FALSE, message=FALSE,warning=FALSE,comment=FALSE}
ggplot(data=starwars_with_me,mapping=aes(x=birth_year, y=BMI))+
  geom_point()+
  geom_smooth()
```
Figure 2. The relationship between age and BMI values


```{r echo = FALSE, message=FALSE,warning=FALSE,comment=FALSE}
ggplot(data=age_below_hundred,mapping=aes(x=birth_year,y=BMI))+
  geom_point()+
  geom_smooth(data=filter(age_below_hundred, birth_year & BMI<100))
```
Figure 3. The relationship between age (<100) and BMI (<100) values
