---
title: "Assignment2"
author: "Ziya YİĞİT"
date: "19 01 2022"
output: word_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) #deleting plot warning messages
```

```{r include = FALSE}
library(tidyverse)
library(knitr)
set.seed(2018556072)
```

### Take a random sample of 1000 observations from this data (you can use sample() function), and save this sample as a new data. Answer the following questions using this sample.

```{r echo=FALSE}
sampfile<-read.csv("D:/covid-data-2020.csv",sep= "\t")
sampfile<- sampfile[sample(nrow(sampfile),1000), ]
```

### Q1 : Calculate the five-number summary statistics (minimum-Q1-median-Q3-maximum) of covid-19 daily new cases for each country within each month. (you can use quantile() function to get the quartiles)
```{r echo=FALSE}
five_number<-sampfile %>%
  group_by(month,location) %>%
  summarize(min=min(new_cases),
            q1=quantile(new_cases,probs=0.25,na.rm=TRUE),
            med=quantile(new_cases,probs=0.50,na.rm=TRUE),
            q3=quantile(new_cases,probs=0.75,na.rm=TRUE),
            max=max(new_cases))
kable(head(five_number,15))
```


### Q2 : Find the highest daily cases and deaths separately for each country. 
```{r echo=FALSE}
highest_case_death<-sampfile %>%
  group_by(location) %>%
  summarize(max_case=max(new_cases,na.rm=TRUE),max_death=max(new_deaths,na.rm=TRUE)) %>%
  arrange(desc(max_case))
kable(highest_case_death) #all of Vatican's max_death datas are NA's so it returns -inf, Monaco had at least one 0 at it so it's 0.
```


### Q3 : Identify the month in which the mean daily cases is the highest for each country.
```{r echo=FALSE}
options(scipen = 100,digits = 5) # getting rid of scientific notations
# not neccessary but makes it look better
meandaily<-sampfile %>%
  group_by(location,month) %>%
  summarize(mean_of_dailycases=mean(new_cases,na.rm=TRUE)) %>%
  arrange(desc(mean_of_dailycases))                       #we arranged most cases 
meandaily<-distinct(meandaily,location, .keep_all = TRUE) #removed other locations with distinct, only top ones are left
kable(meandaily)
```


### Q4 : Select 3 country and plot the distribution of daily cases by month. Use location as clusters (i.e., color=location) to show the difference between countries.
```{r echo=FALSE}
three_country<- filter(sampfile,location ==c("Turkey","Russia","United Kingdom"))
ggplot(data=three_country, mapping=aes(x=month,y=new_cases,color=location)) +
  geom_boxplot(na.rm=FALSE) +
  scale_x_continuous(breaks = seq(0, 12, by = 1)) 

```




---
### Take a random sample of 100 sentences from this data, then split these sentences into words and take each word as a member of a vector. After removing duplicated words (you can use unique() function to remove duplicated words), save this sample as a new data.
```{r}
sampfile<- sample(c(sentences),size=100)
sampfile <- sampfile %>%
  str_split(" ") %>%
  simplify()

sampfile<-str_replace_all(sampfile,"\\.","") #deleting ",.?"
sampfile<-str_replace_all(sampfile,"\\,","")
sampfile<-str_replace_all(sampfile,"\\?","")
sampfile<-str_to_lower(sampfile)             
sampfile<-unique(sampfile)

```


### Q1 : Find words which are starting with “a” and ending with “e”.
```{r echo=FALSE}
ae <- str_subset(sampfile, "^a")
ae <- str_subset(ae, "e$")
```
Words which starts with a and ends with e are :
`r ae`

### Q2 : Calculate the number of words which have more than 3 vowels.
```{r echo=FALSE}
vowelcount<- sampfile[str_count(sampfile,"[aeiou]")>3]
vowelcount_len<-length(vowelcount)
```
There are `r vowelcount_len` words which have more than 3 wovels.
The words which have more than 3 vowels are :
`r vowelcount`
 

### Q3 : List the five longest word in your data
```{r echo=FALSE}
longestwords<-head(sampfile[order(str_count(sampfile),decreasing=TRUE)], 5)
```
Longest five words are :
`r longestwords`

### Q4 : Try to find word(s) which contain any of these words: age, any, day, exp, her, pro, the.
```{r echo=FALSE}
anyofthose <- sampfile[str_detect(sampfile, "her|any|day|exp|age|pro|the")]
```
Words which contain age, any, day, exp, her, pro, the are :
`r anyofthose`















