---
title: "Assignment3"
author: "Ziya YİĞİT"
date: "19 01 2022"
output: word_document
---

```{r include = FALSE}
library(tidyverse)
library(knitr)
set.seed(2018556072)
```

### Q1 : Write a function that finds a prime number(s) given a set of numbers. Your function also provides prime factors of non-prime numbers. The function you will write should return the prime number(s) given in this vector and the non-prime number(s) with their prime factors.

```{r}
prime_func <- function(x) {
  
  primes <- c()
  nonprimes <- c()
  factors <- c()
  
  for (i in x) {
    if (i == 2) {                   #for "2" 
      primes <- c(primes, i)
    } else if ( any(i %% 2:(i-1) == 0)) {   #i from 2 last number checking if we can divide the number
      nonprimes <- c(nonprimes, i)          
      
      factors <- c()
      a = 2
      
      while(i >= a){                #checking if number is smaller than a, then looking for prime factor
        if(i %%a==0){               #if i mod a is 0 add it to factors
          factors<- c(factors,a)    #divide i to a and check if there is lower factor(a-1)
          i <- i/a
          a <- a-1
          
        }
        a <- a+1                    
      }
      
      nonprimes <- c(nonprimes,"[" ,factors, "]")
      
    } else { 
      primes <- c(primes ,i)
    }
  }
  
  
  
  cat("prime nums : " , primes, "\n")
  cat("non prime nums  : ", nonprimes,"\n")
}

```
Lets add test inputs 89, 107, 597, 931, 1083

```{r include=FALSE}
test <- c(89, 107, 597, 931, 1083)
```


The output that we are going to get is this:
```{r echo=FALSE, comment=NA}
prime_func(test)
```


---
### Q2 : Write a function that finds the letter numbers of all words in a given text and sorts the text according to those numbers from words with few letters to words with many letters. Sort the words containing the same number of letters alphabetically.

### For having text, you may use Sentences in tidyverse. Select 5 or 6 sentences randomly from Sentences.

```{r}
sentence_func <- function (x) {            #a function that prints lowest string length words in
                                      # alphabetical order
  x<- x %>%                           
    str_split(" ") %>%
    simplify()
  
  x<-str_replace_all(x,"\\.","")  #Deleting all ",.'?"
  x<-str_replace_all(x,"\\,","")
  x<-str_replace_all(x,"\\'","")
  x<-str_replace_all(x,"\\?","")
  x<-str_to_lower(x)
  
  lengthofwords=c() 
  
  for (i in x){                                     
    lengthofwords = c(lengthofwords,str_length(i)) # finding length of all words
    
  }
  
  alphabetic_order<-sort(x)                                         #sort and order
  final_order<-alphabetic_order[order(str_length(alphabetic_order))]
  
  cat(final_order)
}
```

Let's select 5 or 6 random sentences from tidyverse sentences.

```{r}
sampfile<- sample(c(sentences),size=sample(5:7))
```

What we have is this: `r sampfile`


The output is :
```{r echo=FALSE, comment=NA}
sentence_func(sampfile)
```


